### 2019-01-09 paper/main.tex
Cambios paper

	\section{Introduction}
	\label{sect:introduction}
	Deep learning \cite{lecun2015deep} combines multiple Machine Learning techniques and allows computational models that are composed of numerous processing layers to learn representations of data with various levels of abstraction. These methods have dramatically improved the state-of-the-art in many domains, such as image classification or speech recognition. Deep learning discovers complex structures in large datasets by using the backpropagation algorithm to indicate how a machine should change its internal parameters that are used to compute the representation in each layer from the features in the previous layer.

	The backpropagation algorithm is a stochastic gradient descent algorithm that minimises a predefined loss function. The layer's parameters are updated after backpropagating the loss function gradients through the network. Deep convolutional nets are suited for images, video, speech and audio processing and they have been used extensively in the last years for automatic classification tasks. For the case of images, convolutional layers extract the main features from the pixels of the images and, after that, the fully connected layer classify every sample based on its extracted features. At the output of the convolutional net, a softmax function provides the probabilities of the set of classes predefined in the model for classification tasks. These outputs are compared against the correct values.

	Multiple metrics exist in the literature of machine learning and statistics \cite{cruz2014metrics}\cite{mehdiyev2016evaluating}. Kappa index is a well-known statistic coefficient defined by Cohen \cite{cohen1960coefficient} to measure inter-rater agreement on classifying elements into a set of categories. Later, Weighted Kappa (WK) is a modified version of the Kappa statistic calculated to allow assigning different weights to different levels of aggregation between two variables. Weighted Kappa loss was described in previous work \cite{de2018weighted} and is a cost function that is based on the WK metric. These functions are indicated for problems where different inter-classes weights are assigned, and that work proved that using these functions improves the model performance and reduce the overfitting risk. This kind of problems is associated with ordinal data processing. Those weights are predefined and depend on the type of the chosen WK. In a linear penalisation, the weight is proportional to the distance between the predicted and the real class. In the Quadratic Weighted Kappa (QWK) the penalisation is proportional to the square of the distance. In this work, we will combine the QWK metric and the QWK loss.

	Softmax function is widely used for the output layer in neural networks for classification tasks. It is a simple and efficient function for multi-class problems but not the best when working with ordinal data. In this paper, the Proportional Odds Model (POM) will be used instead of the softmax function. Different link functions will be explored to compare their performance. Also, the influence of other parameters like the learning rate of the optimization algorithm and the batch size will be studied. We will contrast the results obtained with statistical analysis to provide more robust results.

	The experiments will be run using two different ordinal datasets: Diabetic Retinopathy and Adience.

@@

	 Experiments were run with the standard cross-entropy loss and the softmax function too in order to prove the performance improvement of the QWK loss and the Proportional Odds Model. The results of these experiments are analysed in Appendix \ref{app:NominalComparison}.

@@

	\subsection{Statistical analysis}
	In this subsection, a statistical analysis will be performed in order to obtain robust conclusions from the results presented in this section.

@@

@@

	\appendix
	\section{Statistical comparison between nominal and ordinal methods}
	\label{app:NominalComparison}

	The same experiments described in section \ref{sect:experiments} were repeated using the cross-entropy instead of the QWK as loss function for the optimizer and the softmax function instead of the Proportional Odds Model for the output of the network.
	The results for both datasets are shown in Table \ref{table:NominalResults}.

			Adience & $15$ & $10^{-2}$ & $0.0593$ & $0.0713$\\
			Adience & $15$ & $10^{-3}$ & $\textbf{0.8309}$ & $\textbf{0.7575}$\\
			Adience & $15$ & $10^{-4}$ & $0.7867$ & $0.7129$\\
		\end{tabular}
		\caption{Adience results. BS stands for Batch Size, LR for Learning Rate and LF for link function.}
		\label{table:NominalResults}
	\end{table}

	As we did in Section X, we must analyse the effect of the batch size (with values 5, 10 and 15) and the learning rate ($10^{-2}$, $10^{-3}$ and $10^{-4}$) factors have over the WK metric. So, we make an ANOVA II analysis for each dataset.

>>>>

	\section{Introduction}
	\label{sect:introduction}
	Deep learning, introduced by Yann Lecun \cite{lecun2015deep}, combines multiple Machine Learning techniques and allows computational models that are composed of numerous processing layers to learn representations of data with various levels of abstraction. These methods have dramatically improved the state-of-the-art in many domains, such as image classification or speech recognition. Deep learning discovers complex structures in large datasets by using the backpropagation algorithm to indicate how a machine should change its internal parameters that are used to compute the representation in each layer from the features in the previous layer.

	Convolutional neural networks (ConvNets) are designed to process data that comes in the form of multiple arrays. ConvNets are suited for images, video, speech and audio processing, and they have been used extensively in the last years for automatic classification tasks \cite{dong2014learning}\cite{sun2013deep}\cite{ronneberger2015u}. On image classification tasks, each colour channel is represented by a 2D array. In this case, convolutional layers extract the main features from the pixels of the images and, after that, a fully connected layer classify every sample based on its extracted features. At the output of the convolutional net, a softmax function provides the probabilities of the set of classes predefined in the model for classification tasks. These outputs are compared against the correct values.

	The backpropagation algorithm is a stochastic gradient descent algorithm that minimises a predefined loss function. It has been used in the last years in many works \cite{leonard1990improvement}\cite{yu1995dynamic}\cite{krizhevsky2012imagenet}\cite{de2018weighted} for training swallow and deep neural networks. It updates the layer's parameters after backpropagating the loss function gradients through the network. Learning rate hyper-parameter controls the strength of the changes that are applied to those parameters. Some works have checked the importance of finding the optimal value for this parameter \cite{senior2013empirical} and have tried different approaches to try to improve the training process \cite{smith2017cyclical}.

	Batch normalization is another technique that is used for this kind of networks. It reduces the internal covariate shift by normalizing layer inputs. It was presented in 2015 \cite{ioffe2015batch} and gives a critical enhancement to the training phase. Batch size is an important hyper-parameter that should be adjusted as it affects the layer's parameters updates and also the normalization \cite{keskar2016large}\cite{radiuk2017impact}.

	Ordinal classification problems are those where labels are ordered. Multiple metrics exist in the literature of machine learning and statistics \cite{cruz2014metrics}\cite{mehdiyev2016evaluating}. Kappa index is a well-known statistic coefficient defined by Cohen \cite{cohen1960coefficient} to measure inter-rater agreement on classifying elements into a set of categories. Later, Weighted Kappa (WK) is a modified version of the Kappa statistic calculated to allow assigning different weights to different levels of aggregation between two variables. Weighted Kappa loss was described in previous work \cite{de2018weighted} and is a cost function that is based on the WK metric. These functions are indicated for problems where different inter-classes weights are assigned, and that work proved that using these functions improves the model performance and reduce the overfitting risk. This kind of problems is associated with ordinal data processing. Those weights are predefined and depend on the type of the chosen WK. In a linear penalization, the weight is proportional to the distance between the predicted and the real class. In the Quadratic Weighted Kappa (QWK) the penalization is proportional to the square of the distance. In this work, we will combine the QWK metric and the QWK loss.

	Softmax function is widely used for the output layer in neural networks for classification tasks. It is a simple and efficient function for multi-class problems but not the best when working with ordinal data. In this paper, the Proportional Odds Model (POM) \cite{agresti2010analysis} will be used instead of the softmax function. Different link functions will be explored to compare their performance. Also, the influence of other parameters like the learning rate of the optimization algorithm and the batch size will be studied. We will contrast the results obtained with statistical analysis to provide more robust results. An approximated ANOVA III test will be performed because of the limitations of the computational time required to run a higher number of executions.

	The experiments will be run using two different ordinal datasets: Diabetic Retinopathy, that contains high-resolution fundus images related with diabetes disease, and Adience, that is formed of human faces images that are assigned an age range.

@@

	 Experiments were run with the standard cross-entropy loss and the softmax function too in order to prove the performance improvement of the QWK loss and the Proportional Odds Model. The results of these experiments are analysed in Section \ref{app:NominalComparison}.

@@

	\subsection{Statistical analysis}
	\label{sect:statisticalanalysis}
	In this subsection, a statistical analysis will be performed in order to obtain robust conclusions from the results presented in this section.

@@

	\subsection{Statistical comparison between nominal and ordinal methods}
	\label{app:NominalComparison}

	The same experiments described in Section \ref{sect:experiments} were repeated using the cross-entropy instead of the QWK as loss function for the optimizer and the softmax function instead of the Proportional Odds Model for the output of the network.
	The results for both datasets are shown in Table \ref{table:NominalResults}.

			Adience & $15$ & $10^{-2}$ & $0.0593$ & $0.0713$\\
			Adience & $15$ & $10^{-3}$ & $\textbf{0.8309}$ & $\textbf{0.7575}$\\
			Adience & $15$ & $10^{-4}$ & $0.7867$ & $0.7129$\\
		\end{tabular}
		\caption{Nominal method results. BS stands for Batch Size and LR for Learning Rate.}
		\label{table:NominalResults}
	\end{table}

	As we did in Section \ref{sect:statisticalanalysis}, we must analyse the effect of the batch size (with values 5, 10 and 15) and the learning rate ($10^{-2}$, $10^{-3}$ and $10^{-4}$) factors have over the WK metric. So, we make an ANOVA II analysis for each dataset.

@@
